Constraining the High Density Nuclear Symmetry Energy with Pions

### 2019-08-20 chapters/ch_data_analysis.tex
Added some preliminary delta res

\begin{table*}\centering
\ra{1.3}
\begin{tabular}{@{}rrrrcrrrcrrr@{}}\toprule
& \multicolumn{3}{c}{$100 MeV$} & \phantom{abc}& \multicolumn{3}{c}{$100 MeV$} &
\phantom{abc} & \multicolumn{3}{c}{$300 MeV$}\\
\cmidrule{2-4} \cmidrule{6-8} \cmidrule{10-12}
& &\multicolumn{2}{c}{Measured}\\
Particle &\phantom{abc} & Raw & E$\times$B\\
\midrule
p   & 882.8 & d & d & 903.5 & e & e &\phantom{abcdef} & f & f \\
d   & 817.1 & d & d & 898.5 & e & e & 1621.1 & f & f\\
t   & 589.5 & d & d & 887 & e & e & 1612.4 & f & f  \\
$^{3}$He  & 1617.3  & d & d & 1795.2 & e & e & 3236.4 & f & f\\
$^{4}$He  & 1405.6  & d & d & 1782.9 & e & e & 3226.4 & f & f \\
\bottomrule
\end{tabular}
\caption{Summary of expected cocktail. }
\label{tb:cocktailsummary}
\end{table*}

@@

Figure of beam path locations for different beam types
Table of energy loss tables for energies and beam types
Reference appendix for poisson solver 
Tables for ion drift velocity in P-10 Gas reference Sauli
Figure of sDAC or POCA 
Figure of cartoon of what is happening to tracks
Figure of correction map in TPC and MC map 
Figure of before and after correction BDC vs reco momentum
Figure of track residuals before and after?

>>>>

\begin{table*}\centering
\ra{1.3}
\begin{tabular}{@{}rrrrcrrrcrrr@{}}\toprule
& \multicolumn{3}{c}{$100 MeV$} & \multicolumn{3}{c}{$100 MeV$} & \multicolumn{3}{c}{$300 MeV$}\\
\cmidrule{2-4} \cmidrule{6-8} \cmidrule{10-12}
& &\multicolumn{2}{c}{Measured} & & \multicolumn{2}{c}{Measured} & & \multicolumn{2}{c}{Measured}\\
\cmidrule{3-4} \cmidrule{7-8} \cmidrule{11-12}
Particle &\phantom{abc} & Raw & E$\times$B\\
\midrule
p   & 882.8 & d & d & 903.5 & e & e &\phantom{abcdef} & f & f \\
d   & 817.1 & d & d & 898.5 & e & e & 1621.1 & f & f\\
t   & 589.5 & d & d & 887 & e & e & 1612.4 & f & f  \\
$^{3}$He  & 1617.3  & d & d & 1795.2 & e & e & 3236.4 & f & f\\
$^{4}$He  & 1405.6  & d & d & 1782.9 & e & e & 3226.4 & f & f \\
\bottomrule
\end{tabular}
\caption{Summary of expected cocktail. }
\label{tb:cocktailsummary}
\end{table*}

@@

\begin{table}[!htp] % not just 'h!'
\centering % not a center environment
\begin{tabular}{
  @{}
  l
  S[table-format=1.2]
  S[table-format=1.2]
  S[table-format=1.2]
  S[table-format=5.2]
  S[table-format=5.2]
  @{}
}
\toprule
Beam Energy Loss  &
 {${}^{132}$Sn} &
 {${}^{124}$Sn} &
 {${}^{112}$Sn} &
 {${}^{108}$Sn} &
  {Avg.}\\

\midrule
$\si{\kilo\eV\per\centi\meter}$ & 11.2   &.034  &5.43   &  903   &150     \\
\bottomrule
\end{tabular}

\caption{Average energy loss of each beam.}
\label{tb:beameloss}
\end{table}

Reference appendix for poisson solver 
Tables for ion drift velocity in P-10 Gas reference Sauli
Figure of sDAC or POCA 
Figure of cartoon of what is happening to tracks
Figure of correction map in TPC and MC map 
Figure of before and after correction BDC vs reco momentum
Figure of track residuals before and after?
